Vitis amurensis LM

### 2018-12-07 V_amurensis_LM.Rmd
amurensis remove averages

We ran a LM for leaf number and feret diameter ratio.
```{r}
am_fdr_lm <- lm(avg.fdr ~ leaf, data = am_l_means)
summary(am_fdr_lm)
```

```{r}
am_fdr_seg <- segmented(am_fdr_lm,
                       seg.Z = ~ leaf,
                       psi = list(leaf = c(4, 7, 11)))
summary(am_fdr_seg)
```

```{r}
am_fdr_seg$psi
slope(am_fdr_seg)
am_fdr_fitted <- fitted(am_fdr_seg)
am_fdr_model <- data.frame(Leaf = am_l_means$leaf, FDR = am_fdr_fitted)
ggplot(am_fdr_model, aes(x = Leaf, y = FDR)) + geom_line()
am_fdr_lines <- am_fdr_seg$psi[, 2]
am_fdr_mean_break <- am_fdr_plot + geom_vline(xintercept = am_fdr_lines, linetype = "dashed")
am_fdr_mean_break
ggsave("am_fdr_break.png")
```

>>>>

We ran a LM for leaf number and feret diameter ratio.
```{r}
am_fdr_lm <- lm(feret.diameter.ratio ~ leaf, data = amurensis)
summary(am_fdr_lm)
```

```{r}
am_fdr_seg <- segmented(am_fdr_lm,
                       seg.Z = ~ leaf,
                       psi = list(leaf = c(3, 7, 10)))
summary(am_fdr_seg)
```

```{r}
am_fdr_seg$psi
slope(am_fdr_seg)
am_fdr_fitted <- fitted(am_fdr_seg)
am_fdr_model <- data.frame(Leaf = amurensis$leaf, FDR = am_fdr_fitted)
ggplot(am_fdr_model, aes(x = Leaf, y = FDR)) + geom_line()
am_fdr_lines <- am_fdr_seg$psi[, 2]
am_fdr_mean_break <- am_fdr_plot + geom_vline(xintercept = am_fdr_lines, linetype = "dashed")
am_fdr_mean_break
ggsave("am_fdr_break.png")
```

We tested leaf number and tooth area:blade area.
```{r}
am_taba_plot <- ggplot(amurensis, aes(x = leaf, y = tooth.area.blade.area)) + geom_smooth() + theme_classic() + scale_x_continuous(breaks = seq(0, 13, 1))
am_taba_plot <- am_taba_plot +labs(x = "Leaf number",
                               y = "Tooth area:blade area")
am_taba_plot
```

```{r}
am_taba_mean_plot <- ggplot(am_l_means, aes(x = leaf, y = avg.taba)) + geom_line() + theme_classic()
am_taba_mean_plot <- am_taba_mean_plot +labs(x = "Leaf number",
                               y = "Tooth area:blade area")
am_taba_mean_plot
```

We ran a LM for leaf number and tooth area:blade area.
```{r}
am_taba_lm <- lm(tooth.area.blade.area ~ leaf, data = amurensis)
summary(am_taba_lm)
```

```{r}
am_taba_seg <- segmented(am_taba_lm,
                       seg.Z = ~ leaf,
                       psi = list(leaf = c(3, 8, 11)))
summary(am_taba_seg)
```

```{r}
am_taba_seg$psi
slope(am_taba_seg)
am_taba_fitted <- fitted(am_taba_seg)
am_taba_model <- data.frame(Leaf = amurensis$leaf, TABA = am_taba_fitted)
ggplot(am_taba_model, aes(x = Leaf, y = TABA)) + geom_line()
am_taba_lines <- am_taba_seg$psi[, 2]
am_taba_mean_break <- am_taba_plot + geom_vline(xintercept = am_taba_lines, linetype = "dashed")
am_taba_mean_break
ggsave("am_taba_break.png")
```

We tested leaf number and total teeth:perimeter.
```{r}
am_tp_plot <- ggplot(amurensis, aes(x = leaf, y = teeth.perimeter)) + geom_smooth() + theme_classic() + scale_x_continuous(breaks = seq(0, 13, 1))
am_tp_plot <- am_tp_plot +labs(x = "Leaf number",
                               y = "Teeth:perimeter")
am_tp_plot
```

```{r}
am_tp_mean_plot <- ggplot(am_l_means, aes(x = leaf, y = avg.tp)) + geom_line() + theme_classic()
am_tp_mean_plot <- am_tp_mean_plot +labs(x = "Leaf number",
                               y = "Teeth.perimeter")
am_tp_mean_plot
```

We ran a LM for leaf number and teeth:perimeter.
```{r}
am_tp_lm <- lm(teeth.perimeter ~ leaf, data = amurensis)
summary(am_tp_lm)
```

```{r}
am_tp_seg <- segmented(am_tp_lm,
                       seg.Z = ~ leaf,
                       psi = list(leaf = c(3, 8, 11)))
summary(am_tp_seg)
```

```{r}
am_tp_seg$psi
slope(am_tp_seg)
am_tp_fitted <- fitted(am_tp_seg)
am_tp_model <- data.frame(Leaf = amurensis$leaf, TP = am_tp_fitted)
ggplot(am_tp_model, aes(x = Leaf, y = TP)) + geom_line()
am_tp_lines <- am_tp_seg$psi[, 2]
am_tp_mean_break <- am_tp_plot + geom_vline(xintercept = am_tp_lines, linetype = "dashed")
am_tp_mean_break
ggsave("am_tp_break.png")
```

We tested leaf number and total teeth:internal perimeter.
```{r}
am_tip_plot <- ggplot(amurensis, aes(x = leaf, y = teeth.int.perimeter)) + geom_smooth() + theme_classic() + scale_x_continuous(breaks = seq(0, 13, 1))
am_tip_plot <- am_tip_plot +labs(x = "Leaf number",
                               y = "Teeth:internal perimeter")
am_tip_plot
```

```{r}
am_tip_mean_plot <- ggplot(am_l_means, aes(x = leaf, y = avg.tip)) + geom_line() + theme_classic()
am_tip_mean_plot <- am_tip_mean_plot +labs(x = "Leaf number",
                               y = "Teeth.internal perimeter")
am_tip_mean_plot
```

We ran a LM for leaf number and teeth:internal perimeter.
```{r}
am_tip_lm <- lm(teeth.int.perimeter ~ leaf, data = amurensis)
summary(am_tip_lm)
```

```{r}
am_tip_seg <- segmented(am_tip_lm,
                       seg.Z = ~ leaf,
                       psi = list(leaf = c(3, 8, 11)))
summary(am_tip_seg)
```

```{r}
am_tip_seg$psi
slope(am_tip_seg)
am_tip_fitted <- fitted(am_tip_seg)
am_tip_model <- data.frame(Leaf = amurensis$leaf, TIP = am_tip_fitted)
ggplot(am_tip_model, aes(x = Leaf, y = TIP)) + geom_line()
am_tip_lines <- am_tip_seg$psi[, 2]
am_tip_mean_break <- am_tip_plot + geom_vline(xintercept = am_tip_lines, linetype = "dashed")
am_tip_mean_break
ggsave("am_tip_break.png")
```

We tested leaf number and perimeter:area.
```{r}
am_pa_plot <- ggplot(amurensis, aes(x = leaf, y = perimeter.area)) + geom_smooth() + theme_classic() + scale_x_continuous(breaks = seq(0, 13, 1))
am_pa_plot <- am_pa_plot +labs(x = "Leaf number",
                               y = "Perimeter:area")
am_pa_plot
```

```{r}
am_pa_mean_plot <- ggplot(am_l_means, aes(x = leaf, y = avg.pa)) + geom_line() + theme_classic()
am_pa_mean_plot <- am_pa_mean_plot +labs(x = "Leaf number",
                               y = "Perimeter:area")
am_pa_mean_plot
```

We ran a LM for leaf number and perimeter:area.
```{r}
am_pa_lm <- lm(perimeter.area ~ leaf, data = amurensis)
summary(am_pa_lm)
```

```{r}
am_pa_seg <- segmented(am_pa_lm,
                       seg.Z = ~ leaf,
                       psi = list(leaf = c(3, 8, 11)))
summary(am_pa_seg)
```

```{r}
am_pa_seg$psi
slope(am_pa_seg)
am_pa_fitted <- fitted(am_pa_seg)
am_pa_model <- data.frame(Leaf = amurensis$leaf, PA = am_pa_fitted)
ggplot(am_pa_model, aes(x = Leaf, y = PA)) + geom_line()
am_pa_lines <- am_pa_seg$psi[, 2]
am_pa_mean_break <- am_pa_plot + geom_vline(xintercept = am_pa_lines, linetype = "dashed")
am_pa_mean_break
ggsave("am_pa_break.png")
```

We tested leaf number and compactness.
```{r}
am_cp_plot <- ggplot(amurensis, aes(x = leaf, y = compactness)) + geom_smooth() + theme_classic() + scale_x_continuous(breaks = seq(0, 13, 1))
am_cp_plot <- am_cp_plot +labs(x = "Leaf number",
                               y = "Compactness")
am_cp_plot
```

```{r}
am_cp_mean_plot <- ggplot(am_l_means, aes(x = leaf, y = avg.cp)) + geom_line() + theme_classic()
am_cp_mean_plot <- am_cp_mean_plot +labs(x = "Leaf number",
                               y = "Compactness")
am_cp_mean_plot
```

We ran a LM for leaf number and compactness.
```{r}
am_cp_lm <- lm(compactness ~ leaf, data = amurensis)
summary(am_cp_lm)
```

```{r}
am_cp_seg <- segmented(am_cp_lm,
                       seg.Z = ~ leaf,
                       psi = list(leaf = c(3, 8, 11)))
summary(am_cp_seg)
```

```{r}
am_cp_seg$psi
slope(am_cp_seg)
am_cp_fitted <- fitted(am_cp_seg)
am_cp_model <- data.frame(Leaf = amurensis$leaf, CP = am_cp_fitted)
ggplot(am_cp_model, aes(x = Leaf, y = CP)) + geom_line()
am_cp_lines <- am_cp_seg$psi[, 2]
am_cp_mean_break <- am_cp_plot + geom_vline(xintercept = am_cp_lines, linetype = "dashed")
am_cp_mean_break
ggsave("am_cp_break.png")
```

We tested leaf number and total teeth:blade are.
```{r}
am_tba_plot <- ggplot(amurensis, aes(x = leaf, y = teeth.blade.area)) + geom_smooth() + theme_classic() + scale_x_continuous(breaks = seq(0, 13, 1))
am_tba_plot <- am_tba_plot +labs(x = "Leaf number",
                               y = "Total Teeth:Blade Area")
am_tba_plot
```

```{r}
am_tba_mean_plot <- ggplot(am_l_means, aes(x = leaf, y = avg.tba)) + geom_line() + theme_classic()
am_tba_mean_plot <- am_tba_mean_plot +labs(x = "Leaf number",
                               y = "Total Teeth:Blade Area")
am_tba_mean_plot
```

We ran a LM for leaf number and total teeth:blade area.
```{r}
am_tba_lm <- lm(teeth.blade.area ~ leaf, data = amurensis)
summary(am_tba_lm)
```

```{r}
am_tba_seg <- segmented(am_tba_lm,
                       seg.Z = ~ leaf,
                       psi = list(leaf = c(3, 8, 11)))
summary(am_tba_seg)
```

```{r}
am_tba_seg$psi
slope(am_tba_seg)
am_tba_fitted <- fitted(am_tba_seg)
am_tba_model <- data.frame(Leaf = amurensis$leaf, TBA = am_tba_fitted)
ggplot(am_tba_model, aes(x = Leaf, y = TBA)) + geom_line()
am_tba_lines <- am_tba_seg$psi[, 2]
am_tba_mean_break <- am_tba_plot + geom_vline(xintercept = am_tba_lines, linetype = "dashed")
am_tba_mean_break
ggsave("am_tba_break.png")
```

We tested leaf number and total teeth for 2013.
```{r}
am_tt13_plot <- ggplot(am_13, aes(x = leaf, y = total.teeth)) + geom_smooth() + theme_classic() + scale_x_continuous(breaks = seq(0, 12, 1))
am_tt13_plot <- am_tt13_plot +labs(x = "Leaf number",
                               y = "Total Teeth")
am_tt13_plot
```

```{r}
am_tt13_mean_plot <- ggplot(am_tt13_mean, aes(x = leaf, y = avg.tt)) + geom_line() + theme_classic()
am_tt13_mean_plot <- am_tt13_mean_plot +labs(x = "Leaf number",
                               y = "Total Teeth")
am_tt13_mean_plot
```

We ran a LM for leaf number and total teeth in 2013.
```{r}
am_tt13_lm <- lm(total.teeth ~ leaf, data = am_13)
summary(am_tt13_lm)
```

```{r}
am_tt13_seg <- segmented(am_tt13_lm,
                       seg.Z = ~ leaf,
                       psi = list(leaf = c(3, 7, 10)))
summary(am_tt13_seg)
```

```{r}
am_tt13_seg$psi
slope(am_tt13_seg)
am_tt13_fitted <- fitted(am_tt13_seg)
am_tt13_model <- data.frame(Leaf = am_13$leaf, TT = am_tt13_fitted)
ggplot(am_tt13_model, aes(x = Leaf, y = TT)) + geom_line()
am_tt13_lines <- am_tt13_seg$psi[, 2]
am_tt13_mean_break <- am_tt13_plot + geom_vline(xintercept = am_tt13_lines, linetype = "dashed")
am_tt13_mean_break
ggsave("am_tt13_break.png")
```

We tested leaf number and total teeth for 2015.
```{r}
am_tt15_plot <- ggplot(am_15, aes(x = leaf, y = total.teeth)) + geom_smooth() + theme_classic() + scale_x_continuous(breaks = seq(0, 12, 1))
am_tt15_plot <- am_tt15_plot +labs(x = "Leaf number",
                               y = "Total Teeth")
am_tt15_plot
```

```{r}
am_tt15_mean_plot <- ggplot(am_tt15_mean, aes(x = leaf, y = avg.tt)) + geom_line() + theme_classic()
am_tt15_mean_plot <- am_tt15_mean_plot +labs(x = "Leaf number",
                               y = "Total Teeth")
am_tt15_mean_plot
```

We ran a LM for leaf number and total teeth in 2015.
```{r}
am_tt15_lm <- lm(total.teeth ~ leaf, data = am_15)
summary(am_tt15_lm)
```

```{r}
am_tt15_seg <- segmented(am_tt15_lm,
                       seg.Z = ~ leaf,
                       psi = list(leaf = c(3, 7, 10)))
summary(am_tt15_seg)
```

```{r}
am_tt15_seg$psi
slope(am_tt15_seg)
am_tt15_fitted <- fitted(am_tt15_seg)
am_tt15_model <- data.frame(Leaf = am_15$leaf, TT = am_tt15_fitted)
ggplot(am_tt15_model, aes(x = Leaf, y = TT)) + geom_line()
am_tt15_lines <- am_tt15_seg$psi[, 2]
am_tt15_mean_break <- am_tt15_plot + geom_vline(xintercept = am_tt15_lines, linetype = "dashed")
am_tt15_mean_break
ggsave("am_tt15_break.png")
```

We tested leaf number and tooth area:perimeter for 2013.
```{r}
am_tap13_plot <- ggplot(am_13, aes(x = leaf, y = tooth.area.perimeter)) + geom_smooth() + theme_classic() + scale_x_continuous(breaks = seq(0, 13, 1))
am_tap13_plot <- am_tap13_plot +labs(x = "Leaf number",
                               y = "Tooth area: perimeter")
am_tap13_plot
```

```{r}
am_tap13_mean_plot <- ggplot(am_tap13_mean, aes(x = leaf, y = avg.tap)) + geom_line() + theme_classic()
am_tap13_mean_plot <- am_tap13_mean_plot +labs(x = "Leaf number",
                               y = "Tooth area: perimeter")
am_tap13_mean_plot
```

We ran a LM for leaf number and toth area perimeter in 2013.
```{r}
am_tap13_lm <- lm(tooth.area.perimeter ~ leaf, data = am_13)
summary(am_tap13_lm)
```

```{r}
am_tap13_seg <- segmented(am_tap13_lm,
                       seg.Z = ~ leaf,
                       psi = list(leaf = c(3, 7, 10)))
summary(am_tap13_seg)
```

```{r}
am_tap13_seg$psi
slope(am_tap13_seg)
am_tap13_fitted <- fitted(am_tap13_seg)
am_tap13_model <- data.frame(Leaf = am_13$leaf, TAP = am_tap13_fitted)
ggplot(am_tap13_model, aes(x = Leaf, y = TAP)) + geom_line()
am_tap13_lines <- am_tap13_seg$psi[, 2]
am_tap13_mean_break <- am_tap13_plot + geom_vline(xintercept = am_tap13_lines, linetype = "dashed")
am_tap13_mean_break
ggsave("am_tap13_break.png")
```

We tested leaf number and tooth area:perimeter for 2015.
```{r}
am_tap15_plot <- ggplot(am_15, aes(x = leaf, y = tooth.area.perimeter)) + geom_smooth() + theme_classic() + scale_x_continuous(breaks = seq(0, 12, 1))
am_tap15_plot <- am_tap15_plot +labs(x = "Leaf number",
                               y = "Tooth area:perimeter")
am_tap15_plot
```

```{r}
am_tap15_mean_plot <- ggplot(am_tap15_mean, aes(x = leaf, y = avg.tap)) + geom_line() + theme_classic()
am_tap15_mean_plot <- am_tap15_mean_plot +labs(x = "Leaf number",
                               y = "Tooth area:perimeter")
am_tap15_mean_plot
```

We ran a LM for leaf number and tooth area:perimeter in 2015.
```{r}
am_tap15_lm <- lm(tooth.area.perimeter ~ leaf, data = am_15)
summary(am_tap15_lm)
```

```{r}
am_tap15_seg <- segmented(am_tap15_lm,
                       seg.Z = ~ leaf,
                       psi = list(leaf = c(3, 7, 10)))
summary(am_tap15_seg)
```

```{r}
am_tap15_seg$psi
slope(am_tap15_seg)
am_tap15_fitted <- fitted(am_tap15_seg)
am_tap15_model <- data.frame(Leaf = am_15$leaf, TAP = am_tap15_fitted)
ggplot(am_tap15_model, aes(x = Leaf, y = TAP)) + geom_line()
am_tap15_lines <- am_tap15_seg$psi[, 2]
am_tap15_mean_break <- am_tap15_plot + geom_vline(xintercept = am_tap15_lines, linetype = "dashed")
am_tap15_mean_break
ggsave("am_tap15_break.png")
```

We tested leaf number and tooth area:internal perimeter for 2013.
```{r}
am_taip13_plot <- ggplot(am_13, aes(x = leaf, y = tooth.area.int.perimeter)) + geom_smooth() + theme_classic() + scale_x_continuous(breaks = seq(0, 12, 1))
am_taip13_plot <- am_taip13_plot +labs(x = "Leaf number",
                               y = "Tooth area: internal perimeter")
am_taip13_plot
```

```{r}
am_taip13_mean_plot <- ggplot(am_taip13_mean, aes(x = leaf, y = avg.taip)) + geom_line() + theme_classic()
am_taip13_mean_plot <- am_taip13_mean_plot +labs(x = "Leaf number",
                               y = "Tooth area:internal perimeter")
am_taip13_mean_plot
```

We ran a LM for leaf number and toth area: internal perimeter in 2013.
```{r}
am_taip13_lm <- lm(tooth.area.int.perimeter ~ leaf, data = am_13)
summary(am_taip13_lm)
```

```{r}
am_taip13_seg <- segmented(am_taip13_lm,
                       seg.Z = ~ leaf,
                       psi = list(leaf = c(3, 7, 10)))
summary(am_taip13_seg)
```

```{r}
am_taip13_seg$psi
slope(am_taip13_seg)
am_taip13_fitted <- fitted(am_taip13_seg)
am_taip13_model <- data.frame(Leaf = am_13$leaf, TAIP = am_taip13_fitted)
ggplot(am_taip13_model, aes(x = Leaf, y = TAIP)) + geom_line()
am_taip13_lines <- am_taip13_seg$psi[, 2]
am_taip13_mean_break <- am_taip13_plot + geom_vline(xintercept = am_taip13_lines, linetype = "dashed")
am_taip13_mean_break
ggsave("am_taip13_break.png")
```

We tested leaf number and tooth area:internal perimeter for 2015.
```{r}
am_taip15_plot <- ggplot(am_15, aes(x = leaf, y = tooth.area.int.perimeter)) + geom_smooth() + theme_classic() + scale_x_continuous(breaks = seq(0, 13, 1))
am_taip15_plot <- am_taip15_plot +labs(x = "Leaf number",
                               y = "Tooth area:internal perimeter")
am_taip15_plot
```

```{r}
am_taip15_mean_plot <- ggplot(am_taip15_mean, aes(x = leaf, y = avg.taip)) + geom_line() + theme_classic()
am_taip15_mean_plot <- am_taip15_mean_plot +labs(x = "Leaf number",
                               y = "Tooth area:internal perimeter")
am_taip15_mean_plot
```

We ran a LM for leaf number and tooth area:internal perimeter in 2015.
```{r}
am_taip15_lm <- lm(tooth.area.int.perimeter ~ leaf, data = am_15)
summary(am_taip15_lm)
```

```{r}
am_taip15_seg <- segmented(am_taip15_lm,
                       seg.Z = ~ leaf,
                       psi = list(leaf = c(3, 7, 10)))
summary(am_taip15_seg)
```

```{r}
am_taip15_seg$psi
slope(am_taip15_seg)
am_taip15_fitted <- fitted(am_taip15_seg)
am_taip15_model <- data.frame(Leaf = am_15$leaf, TAIP = am_taip15_fitted)
ggplot(am_taip15_model, aes(x = Leaf, y = TAIP)) + geom_line()
am_taip15_lines <- am_taip15_seg$psi[, 2]
am_taip15_mean_break <- am_taip15_plot + geom_vline(xintercept = am_taip15_lines, linetype = "dashed")
am_taip15_mean_break
ggsave("am_taip15_break.png")
```

We tested leaf number and average tooth area for 2013.
```{r}
am_ata13_plot <- ggplot(am_13, aes(x = leaf, y = average.tooth.area)) + geom_smooth() + theme_classic() + scale_x_continuous(breaks = seq(0, 13, 1))
am_ata13_plot <- am_ata13_plot +labs(x = "Leaf number",
                               y = "Average tooth area")
am_ata13_plot
```

```{r}
am_ata13_mean_plot <- ggplot(am_ata13_mean, aes(x = leaf, y = avg.ata)) + geom_line() + theme_classic()
am_ata13_mean_plot <- am_ata13_mean_plot +labs(x = "Leaf number",
                               y = "Average tooth area")
am_ata13_mean_plot
```

We ran a LM for leaf number and average tooth area in 2013.
```{r}
am_ata13_lm <- lm(average.tooth.area ~ leaf, data = am_13)
summary(am_ata13_lm)
```

```{r}
am_ata13_seg <- segmented(am_ata13_lm,
                       seg.Z = ~ leaf,
                       psi = list(leaf = c(3, 7, 10)))
summary(am_ata13_seg)
```

```{r}
am_ata13_seg$psi
slope(am_ata13_seg)
am_ata13_fitted <- fitted(am_ata13_seg)
am_ata13_model <- data.frame(Leaf = am_13$leaf, ATA = am_ata13_fitted)
ggplot(am_ata13_model, aes(x = Leaf, y = ATA)) + geom_line()
am_ata13_lines <- am_ata13_seg$psi[, 2]
am_ata13_mean_break <- am_ata13_plot + geom_vline(xintercept = am_ata13_lines, linetype = "dashed")
am_ata13_mean_break
ggsave("am_ata13_break.png")
```

We tested leaf number and average tooth area for 2015.
```{r}
am_ata15_plot <- ggplot(am_15, aes(x = leaf, y = average.tooth.area)) + geom_smooth() + theme_classic() + scale_x_continuous(breaks = seq(0, 13, 1))
am_ata15_plot <- am_ata15_plot +labs(x = "Leaf number",
                               y = "Average tooth area")
am_ata15_plot
```

```{r}
am_ata15_mean_plot <- ggplot(am_ata15_mean, aes(x = leaf, y = avg.ata)) + geom_line() + theme_classic()
am_ata15_mean_plot <- am_ata15_mean_plot +labs(x = "Leaf number",
                               y = "Average tooth area")
am_ata15_mean_plot
```

We ran a LM for leaf number and average tooth area in 2015.
```{r}
am_ata15_lm <- lm(average.tooth.area ~ leaf, data = am_15)
summary(am_ata15_lm)
```

```{r}
am_ata15_seg <- segmented(am_ata15_lm,
                       seg.Z = ~ leaf,
                       psi = list(leaf = c(3, 7, 10)))
summary(am_ata15_seg)
```

```{r}
am_ata15_seg$psi
slope(am_ata15_seg)
am_ata15_fitted <- fitted(am_ata15_seg)
am_ata15_model <- data.frame(Leaf = am_15$leaf, ATA = am_ata15_fitted)
ggplot(am_ata15_model, aes(x = Leaf, y = ATA)) + geom_line()
am_ata15_lines <- am_ata15_seg$psi[, 2]
am_ata15_mean_break <- am_ata15_plot + geom_vline(xintercept = am_ata15_lines, linetype = "dashed")
am_ata15_mean_break
ggsave("am_ata15_break.png")
```

We tested leaf number and perimeter ratio for 2013.
```{r}
am_pr13_plot <- ggplot(am_13, aes(x = leaf, y = perimeter.ratio)) + geom_smooth() + theme_classic() + scale_x_continuous(breaks = seq(0, 13, 1))
am_pr13_plot <- am_pr13_plot +labs(x = "Leaf number",
                               y = "Perimeter ratio")
am_pr13_plot
```

```{r}
am_pr13_mean_plot <- ggplot(am_pr13_mean, aes(x = leaf, y = avg.pr)) + geom_line() + theme_classic()
am_pr13_mean_plot <- am_pr13_mean_plot +labs(x = "Leaf number",
                               y = "Perimeter ratio")
am_pr13_mean_plot
```

We ran a LM for leaf number and perimeter ratio in 2013.
```{r}
am_pr13_lm <- lm(perimeter.ratio ~ leaf, data = am_13)
summary(am_pr13_lm)
```

```{r}
am_pr13_seg <- segmented(am_pr13_lm,
                       seg.Z = ~ leaf,
                       psi = list(leaf = c(3, 7, 10)))
summary(am_pr13_seg)
```

```{r}
am_pr13_seg$psi
slope(am_pr13_seg)
am_pr13_fitted <- fitted(am_pr13_seg)
am_pr13_model <- data.frame(Leaf = am_13$leaf, PR = am_pr13_fitted)
ggplot(am_pr13_model, aes(x = Leaf, y = PR)) + geom_line()
am_pr13_lines <- am_pr13_seg$psi[, 2]
am_pr13_mean_break <- am_pr13_plot + geom_vline(xintercept = am_pr13_lines, linetype = "dashed")
am_pr13_mean_break
ggsave("am_pr13_break.png")
```

We tested leaf number and perimeter ratio for 2015.
```{r}
am_pr15_plot <- ggplot(am_15, aes(x = leaf, y = perimeter.ratio)) + geom_smooth() + theme_classic() + scale_x_continuous(breaks = seq(0, 13, 1))
am_pr15_plot <- am_pr15_plot +labs(x = "Leaf number",
                               y = "Perimeter ratio")
am_pr15_plot
```

```{r}
am_pr15_mean_plot <- ggplot(am_pr15_mean, aes(x = leaf, y = avg.pr)) + geom_line() + theme_classic()
am_pr15_mean_plot <- am_pr15_mean_plot +labs(x = "Leaf number",
                               y = "Perimeter ratio")
am_pr15_mean_plot
```

We ran a LM for leaf number and average tooth area in 2015.
```{r}
am_pr15_lm <- lm(perimeter.ratio ~ leaf, data = am_15)
summary(am_pr15_lm)
```

```{r}
am_pr15_seg <- segmented(am_pr15_lm,
                       seg.Z = ~ leaf,
                       psi = list(leaf = c(3, 7, 10)))
summary(am_pr15_seg)
```

```{r}
am_pr15_seg$psi
slope(am_pr15_seg)
am_pr15_fitted <- fitted(am_pr15_seg)
am_pr15_model <- data.frame(Leaf = am_15$leaf, PR = am_pr15_fitted)
ggplot(am_pr15_model, aes(x = Leaf, y = PR)) + geom_line()
am_pr15_lines <- am_pr15_seg$psi[, 2]
am_pr15_mean_break <- am_pr15_plot + geom_vline(xintercept = am_pr15_lines, linetype = "dashed")
am_pr15_mean_break
ggsave("am_pr15_break.png")
```

We tested leaf number and shape factor for 2013.
```{r}
am_sf13_plot <- ggplot(am_13, aes(x = leaf, y = shape.factor)) + geom_smooth() + theme_classic() + scale_x_continuous(breaks = seq(0, 13, 1))
am_sf13_plot <- am_sf13_plot +labs(x = "Leaf number",
                               y = "Shape factor")
am_sf13_plot
```

```{r}
am_sf13_mean_plot <- ggplot(am_sf13_mean, aes(x = leaf, y = avg.sf)) + geom_line() + theme_classic()
am_sf13_mean_plot <- am_sf13_mean_plot +labs(x = "Leaf number",
                               y = "Shape factor")
am_sf13_mean_plot
```

We ran a LM for leaf number and shape factor in 2013.
```{r}
am_sf13_lm <- lm(shape.factor ~ leaf, data = am_13)
summary(am_sf13_lm)
```

```{r}
am_sf13_seg <- segmented(am_sf13_lm,
                       seg.Z = ~ leaf,
                       psi = list(leaf = c(3, 7, 10)))
summary(am_sf13_seg)
```

```{r}
am_sf13_seg$psi
slope(am_sf13_seg)
am_sf13_fitted <- fitted(am_sf13_seg)
am_sf13_model <- data.frame(Leaf = am_13$leaf, SF = am_sf13_fitted)
ggplot(am_sf13_model, aes(x = Leaf, y = SF)) + geom_line()
am_sf13_lines <- am_sf13_seg$psi[, 2]
am_sf13_mean_break <- am_sf13_plot + geom_vline(xintercept = am_sf13_lines, linetype = "dashed")
am_sf13_mean_break
ggsave("am_sf13_break.png")
```

We tested leaf number and shape factor for 2015.
```{r}
am_sf15_plot <- ggplot(am_15, aes(x = leaf, y = shape.factor)) + geom_smooth() + theme_classic() + scale_x_continuous(breaks = seq(0, 13, 1))
am_sf15_plot <- am_sf15_plot +labs(x = "Leaf number",
                               y = "Shape factor")
am_sf15_plot
```

```{r}
am_sf15_mean_plot <- ggplot(am_sf15_mean, aes(x = leaf, y = avg.sf)) + geom_line() + theme_classic()
am_sf15_mean_plot <- am_sf15_mean_plot +labs(x = "Leaf number",
                               y = "Shape factor")
am_sf15_mean_plot
```

We ran a LM for leaf number and shape factor in 2015.
```{r}
am_sf15_lm <- lm(shape.factor ~ leaf, data = am_15)
summary(am_sf15_lm)
```

```{r}
am_sf15_seg <- segmented(am_sf15_lm,
                       seg.Z = ~ leaf,
                       psi = list(leaf = c(3, 7, 10)))
summary(am_sf15_seg)
```

```{r}
am_sf15_seg$psi
slope(am_sf15_seg)
am_sf15_fitted <- fitted(am_sf15_seg)
am_sf15_model <- data.frame(Leaf = am_15$leaf, SF = am_ata15_fitted)
ggplot(am_sf15_model, aes(x = Leaf, y = SF)) + geom_line()
am_sf15_lines <- am_sf15_seg$psi[, 2]
am_sf15_mean_break <- am_sf15_plot + geom_vline(xintercept = am_sf15_lines, linetype = "dashed")
am_sf15_mean_break
ggsave("am_sf15_break.png")
```
